DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-24 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
We would first like to thank the reviewers for your valuable feedback which helped us to improve the analysis of the proposed method and the overall presentation of the paper.
Due to space constraints with significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{http://www.texample.net/tikz/resources/}{new version of the paper}. we address only the major criticisms below.

We have rewritten our contributions in Section 1 and make our contributions more clearly.

We have restructured our methodology in section 3 and further explain the intuition behind the chosen architecture.

\subsection{Common}

\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g. center of detected bounding box).}

\noindent We have re-implemented Social-LSTM for 2D data. blablabla details...

\noindent \textbf{1) Unlike stated in the paper, vehicle tracking in images has been studied for years. There are summary papers (e.g. VEHICLE DETECTION AND TRACKING TECHNIQUES: A CONCISE REVIEW Raad Ahmed Hadi1,2 , Ghazali Sulong1 and Loay Edwar George, SIPIJ). There is no mention of prior art.}
\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}
\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}

We have restructured our related works. Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``RNN for sequence prediction" part.

@@

\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
\noindent \textbf{It is not clear if the dataset is released with the paper.}

\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}

\noindent Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize \textbf{\emph{continuous video streams}} for the prediction problems. We would like to release publicly-available prediction challenge based on Synthia to spur future research upon paper publication.

\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?}
\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
\noindent \textbf{They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}

\noindent  Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking. In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame. Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations. This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists). Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting. Hence the tracker is served solely as instance associator for the traffic participant.

\subsection{R1}
\noindent \textbf{3) 3 very similar LSTMs with different input}
\noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}

\noindent Explain the intuition....

@@

\subsection{R2}

\noindent \textbf{SocialLSTM used ``Avg. disp. Error", ``Avg. non-linear disp. error" , and ``final disp. Error" What was the justification for the metrics the authors chose?}

\noindent The ``average displacement error" is essentially the same as the ``center error" in Tab.3 of our paper and the subtle difference is that the former is in unit space and the latter is in pixel space. Similarly ``Final displacement error" is the last frame's ``center error" is unit space. ``average non-linear displacement error"

@@

 \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to “predict car’s future odometry given previous egomotion visual input”. But the paper is about prediction of other vehicles’ trajectories, not about predicting one’s own car odometry (which is different).}

\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}

\subsection{R3}
\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here. In general a lot of methodology detail is actually in section 4 (implementation details). Maybe consider reorganizing a little bit.}

\noindent We thank the reviewer for the very meticulous review.  We have refined our contributions in the introduction section and restructured the methodology section. We have also corrected the grammatical misuses accordingly.

\noindent \textbf{In a real car accurate depth information might not be available. Also, tracking and semantic segmentation results in the real world will probably be noisier than for synthetic data. Experiments on real data would make the results much stronger.}
\noindent \textbf{Do you think the results you obtained with the Synthia data will transfer to real-world data?}
\noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with ‘real’ physics and photo-realism similar to Synthia. It would be interesting to implement this system and evaluate ‘real-world’ performance.}

\noindent We have indeed noticed the recently released photo-realistic simulators CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV}. And we found that CARLA is especially suited as a further extension to verify our proposed system due to the availability of continuous video streams and ground truth segmentation. In terms of transferring to real-world data, from the semantic segmentation results of Synthia, we have observed that model trained on synthetic dataset produced good segmentations by itself on real datasets, and dramatically boosted accuracy in combination with real data. Hence, we believe the hybrid of synthetic data and real-world data would be the most data efficient and promising way for the model generalization. Model verification on public real-world datasets, e.g., Comma.ai~\cite{santana2016learning} Udacity~\cite{udacity} dataset would be our forthcoming imminent works.

### 2018-01-24 paper/cvpr2018/cvpr2018_3790.tex
paper writing. TODO: writing exp section with social lstm.

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage{booktabs}
%\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tabu,multirow}
\DeclareCaptionLabelFormat{noname}{#2}
\captionsetup[algorithm]{labelformat=noname}

@@

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict the car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics) to further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
In addition, the scene parsing results contain quite some spurious information.
Existing methods for scene parsing also mainly focus on static images.
However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by a sequence of input frames instead of simply one static frame.
Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicle trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

% Then have a final paragraph or subsection: "Summary of Contributions". It should list the major contributions in bullet form, mentioning in which sections they can be found. This material doubles as an outline of the rest of the paper, saving space and eliminating redundancy.
In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction as shown in Fig.~\ref{fig:pull_figure}.Our contributions are as follows:

\begin{itemize}

\item We verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception. The proposed system stems from the issue of human driver reaction time in the autonomous driving context.

\item We present a novel ``tracking-by-detection" framework for robust vehicle tracking. By updating tracker's target representation via detection association, we also solve the problem of instance association between frames.

\item We design various temporal models for the problem of predicting future trajectories based on historical data. Results show that the temporal model generating intermediate representation performs better than the frame-to-frame based temporal model.

\item We demonstrate the effectiveness of using ``privileged information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.

\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.

\end{itemize}

@@

%\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%\subsection{Traffic participants detection and tracking: object detection and instance association}
\subsection{Object detection}
Vehicle detection is one key component of an autonomous driving system. Typical algorithms output bounding boxes on detected vehicles.
A lot of progess has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
Modern object detectors based on these networks -- such as the line of works on the R-CNN~\cite{girshick2014rich},
Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
% Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
% However, after the proposal of
 R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
 % At the beginning, R-CNN is a step-by-step and inefficient method. Then,
  SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features. Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build an end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

@@

\subsection{Instance association}
Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.  3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the present of large displacement or local ambiguities.
%Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
However, a total runtime of 10 minutes per frame is way too prohibitive for the deployment in the context of autonomous driving.
To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking.
Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
Built upon their seminal work, there has been a plethora of recent improvements~\cite{wang2016stct, wang2015visual, hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{
        The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data obtained from the host car. Historical information is extracted by detection \& tracking. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into our LSTM model to predict future trajectories.}

        \label{fig:framework}
\end{figure*}

\subsection{Recurrent neural networks}

Recent advances in recurrent neural network for modeling visual sequential data are also related to our work.
%Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
Mostly, RNN is trained as a pilot network in the context of behaviour reflex approaches.
Long Short Term Memory (LSTM) cells are usually exploited as one intermediate component of an end-to-end driving model.
 A combination of a fully-convolutional network and an LSTM is proposed in~\cite{xu2017end} to learn from large-scale vehicle action data. Their goal is to predict future egomotion including multi-modal discrete and continuous driving behaviors.
 Inverse turning radius is predicted by a LSTM network in~\cite{kim2017interpretable}: they generate a heat map of attention at each time step conditioned on the previous hidden states and a current convolutional feature cube  to produce more succinct visual explanations. ~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation. In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.

\subsection{Dataset for autonomous driving}

Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community. A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\subsection{3D Traffic Participants Trajectory Prediction}

We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
Our work is most related to~\cite{xu2017end} where the problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $H=\{h_t^p\}, t=1,\dots, T $ with auxiliary information $ A=\{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $J=\{j_t^p\}, t={T+1}, \ldots$:

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage{booktabs}
%\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tabu,multirow}
\usepackage[toc,page]{appendix}
\DeclareCaptionLabelFormat{noname}{#2}
\captionsetup[algorithm]{labelformat=noname}

@@

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict the car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
We also show the effectiveness of combining various levels of abstractions(e.g., scene semantics, detection bounding boxes) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ \small{
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
In addition, the scene parsing results contain quite some spurious information.
Existing methods for scene parsing also mainly focus on static images.
However, autonomous driving is intrinsically a dynamic problem. Human drivers make decisions by a sequence of input frames instead of one static frame.
Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicle trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories by obeying a large number of common sense rulesp (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between the traditional visual tracking community and the current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

% Then have a final paragraph or subsection: "Summary of Contributions". It should list the major contributions in bullet form, mentioning in which sections they can be found. This material doubles as an outline of the rest of the paper, saving space and eliminating redundancy.
We address this issue through building a system that takes advantage of multiple streams with various levels of abstraction.
In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction as shown in Fig.~\ref{fig:pull_figure}.Our main contributions are as follows:
\begin{itemize}
\itemsep0em
\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia}\footnote{Dataset will be released upon paper publication.} and verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception.

\item We take advantage of various levels of abstractions from multiple streams via recurrent network based temporal models and demonstrate the effectiveness of using ``auxiliary information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.

\item Preliminary results by incorporating ``social" factor demonstrate the potential of learning common sense rules with neighboring traffic participants in complex real world  environment.

\end{itemize}
%\begin{itemize}
%
%\item We verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception. The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
%
%\item We present a novel ``tracking-by-detection" framework for robust vehicle tracking. By updating tracker's target representation via detection association, we also solve the problem of instance association between frames.
%
%\item We design various temporal models for the problem of predicting future trajectories based on historical data. Results show that the temporal model generating intermediate representation performs better than the frame-to-frame based temporal model.
%
%\item We demonstrate the effectiveness of using ``privileged information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.
%
%
%\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
%
%\end{itemize}

@@

%\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%\subsection{Traffic participants detection and tracking: object detection and instance association}
\noindent \textbf{Traffic participants detection} Traffic participants detection is one key component of an autonomous driving system. Vehicle detection has been well studied for static high-way mounted cameras: ~\cite{hadi2014vehicle} present a concise overview of image processing methods and analysis tools before the ``deep learning eras".
%Typical algorithms output bounding boxes on detected vehicles.
A lot of progress has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
Modern object detectors~\cite{girshick2014rich, Girshick2015Fast, ren2015faster_nips, He2015Spatial, he2017mask, redmon2016you, liu2016ssd} are now good enough to be deployed in a consumer products. Faster R-CNN~\cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN~\cite{Girshick2015Fast} to build an end-to-end architecture. SSD \cite{liu2016ssd} similarly uses a series of boxes and directly gives the probability for each object class.

Typical algorithms output bounding boxes on detected objects for a static image. And the deep neural nets can be transferred and fine-tuned to another set of classes for traffic participants  we actually care about in the context of autonomous driving.
% on the R-CNN~\cite{girshick2014rich},
%Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
% Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
% However, after the proposal of
%R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
%% At the beginning, R-CNN is a step-by-step and inefficient method. Then,
%SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features. Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build an end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

@@

\noindent \textbf{Instance association} Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.  3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the presence of large displacement or local ambiguities.
%Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
However, a total runtime of 10 minutes per frame is computationally prohibitive for the real-time deployment.
To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking.
Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
Built upon their seminal work, there has been a plethora of recent improvements~\cite{hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.

Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking. In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame. Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations. This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists). Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting. Hence the tracker is served solely as instance associator for the traffic participant.

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{
        \small{The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car. Target vehicles' sequential bounding boxes are extracted by detection \& tracking module. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
        }
        \label{fig:framework}
\end{figure*}
%\noindent \textbf{RNN for sequence prediction}

%Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
\noindent \textbf{Activity forecasting} Activity forecasting is the task of predicting the motion or the action to be carried out by objects in a video. 
A body of work~\cite{chalasani2013deep, clark2013whatever, egner2010expectation} explores various hierarchical models in face of different quality of data representation. 
 Recently recurrent neural networks (RNN) and their variants including Long Short Term Memory (LSTM)~\cite{hochreiter1997long} and Gated Recurrent Units (GRU)~\cite{chung2014empirical} have proven to be very successful for sequence prediction tasks.
 An action-conditioned video prediction model~\cite{finn2016unsupervised} that explicitly models pixel motion, by predicting a distribution over pixel motion from previous frames is proposed to learn from unsupervised video data.
 %The discrepancy between training and inference can yield errors that can accumulate quickly along the generated sequence when using a recurrent neural network.p
 A curriculum learning strategy is proposed in~\cite{bengio2015scheduled} to gently change the training process from a fully guided scheme using the true previous token, towards a less guided scheme which mostly uses the generated token instead. 
A combination of a fully-convolutional network and an LSTM is proposed in~\cite{xu2017end} to learn from large-scale vehicle action data and  is trained as a pilot network in the context of behaviour reflex approaches. Their goal is to predict future egomotion including multi-modal discrete and continuous driving behaviors.
Inverse turning radius is predicted by a LSTM network in~\cite{kim2017interpretable}: a heat map of attention is generated at each time step conditioned on the previous hidden states as a more succinct visual explanations.

More recent works also attempt to take the ``social factor" into consideration. Social-LSTM~\cite{alahi2016social} focus on modeling dynamics crowd interactions for path prediction by introducing a ``social tensor" from a spatial-temporal neighborhood. Based on the social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
%~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation. In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.

\noindent \textbf{Datasets for autonomous driving} Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community.
CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV} are two recent endeavours that take advantage of simulated environment to support development, training and validation of autonomous urban driving systems.
A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is collected for investigating how useful synthetic images can be for semantic segmentation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\subsection{Problem formulation}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
        \caption{
        \small{Illustrations of three temporal networks. $\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.  Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with extra auxiliary information as input $\mathcal{A}$. $\mathcal{S}$ is the social tensor that can be inserted into existing recurrent networks.}
        }
        \label{fig:lstm}
\end{figure}
